Particle Swarm Optimization for Passivation of Steel Substrate with Zirconium Oxide

### 2024-10-29 doc/presentations/defensio/defense.tex
fix formatting
improve formulas for metrics
work in feedback by ditus

	%% ====== title page ======
	\title{Particle Swarm Optimization for Chemical Passivation of Steel Substrate with Zirconium Oxide} %% Presentation Title
	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
	\newcommand{\gPath}{figures/}									%% set graphics path
	\newcommand{\graphicsTitleBackground}{title}    %% Filename of background graphic

@@

\usepackage{siunitx}
\usepackage{chemformula}
\usepackage{upgreek}

@@

%% ====== Slides ======
%TODO: - read aqua/good recipe/mars paper
%01. title slide 
	% - aufhänger
	% - AI and PV
	% - Lab or Computer 
%02. agenda
\begin{frame}{Agenda}
	\vspace{2em}
	\begin{itemize}
		\item Motivation: CIGS substrate
		\item Methods: recipe and sample preparation
		\item Calculation: PSO and data pipeline
		\item Results: materials and optimisation
	\end{itemize}
\end{frame}
	% - more like process  from beginning to finish
%03. background info
	% - PV CIGS substrate % https://de.wikipedia.org/wiki/Chalkopyrit
	% https://en.wikipedia.org/wiki/Copper_indium_gallium_selenide_solar_cell
\begin{graphicsFrame}{Copper Indium Gallium Selenide (CIGS)}{}{0.37}{left}{cigs}{U. Rau, H.W. Schock (2013) "Solar Cells"}
\begin{table}
	\resizebox{.95\textwidth}{!}{
    \begin{tabular}{cccc}
        \hline\hline
		Empirical Formula&   Band Gap [\SI{}{\electronvolt}]\\
        \hline
		\ch{CuInSe2}&  1.04\\
		\ch{CuGaSe2}&  1.7\\
		\ch{CuInS2}&  1.5\\
		\ch{CuGaS2}&  1.55\\
        \hline\hline
    \end{tabular}
}
    \caption{Band gaps of different chalcopyrites (K. Mertens 2015 "Photovoltaik")}
\end{table}
\end{graphicsFrame}

@@

\begin{graphicsFrame}{CIGS modules}{}{0.1}{}{cigs_mod}{}
\end{graphicsFrame}

%04. hypothesis 
%05. manual methods
	% - precursor solution preparation 
		% Anwar 2017 https://iopscience.iop.org/article/10.1088/1757-899X/257/1/012087
		% Hu 2016 https://www.sciencedirect.com/science/article/abs/pii/S0272884216312548
\begin{frame}{Recipes for Precursor Solutions}
	\begin{figure}
		\includegraphics[width=.79\textwidth]{figures/huetal.png}
	\end{figure}
	\pause
\begin{table}[h]
	\center
	\label{tab:rec2}
	\begin{tabular}{rlllll}
		\hline
		recipe	&1F		&2F		&3F		&4F		&5F		\\
		\hline
		\ch{BuOH} [ml]	&4.95	&4.9	&4.85	&4.8	&4.75	\\
		\ch{ZrPro} [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
		\ch{AcAc} [ml]	&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
		\ch{IPO}/\ch{AcOH} [ml]	&2		&2		&2		&2		&2		\\
		\hline
	\end{tabular}
	%\caption{Composition of different buthanolic solutions}
\end{table}
\end{frame}

	% - doctor blading = tape castig 
	% - calcination 
\begin{frame}{Tape casting and Calcination}
	\begin{figure}
		\center
		\includegraphics[width=.65\textwidth]{figures/tc.jpg}
	\end{figure}
\end{frame}
%	\begin{itemize}
%		\item doctor blading construction 
%		\item calcination infos (max temperatur, heating rate)
%	\end{itemize}
%\end{frame}
	% - sputtering contacts
	% - measuring current-voltage characteristics
\begin{frame}{Sputtering and I-V measurement}
	\begin{figure}
		\includegraphics<1>[width=.63\textwidth]{figures/sample1.jpg}
		\includegraphics<2>[width=.63\textwidth]{figures/sample2.jpg}
		\includegraphics<3>[width=.63\textwidth]{figures/sample3.jpg}
	\end{figure}
\end{frame}

%06. computational pipeline 
\begin{frame}{Pin Hole Density and Leakage Current}
	\vspace{2em}
	\begin{itemize}
		\item Pin Hole Density 
			\begin{itemize}
				\item $
%	\rho = \frac{n_{-}}{(n_{-} + n_{+})}
	\rho = \sum_i^N \frac{s_i}{N}
					$
				\item $
	s_i = \begin{cases}
        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
	\end{cases}
					$
			\end{itemize}
	\vspace{0.5em}
		\item Leakage Current 
			\begin{itemize}
				\item $
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	$
			\end{itemize}
	\end{itemize}
\end{frame}
	% - PSO + MARS = EMMA
	% PSO https://doi.org/10.1109/CEC.2010.5586165
\begin{graphicsFrame}{Particle Swarm Optimisation}{}{0.37}{right}{swarm}{}
	\vspace{2em}
	\begin{itemize}
		\item ispired by bird flocks and fish schools %# swarm intelligence
		\item iterative process % nice bcs sample prep takes long time 
		\item particles: 
			\begin{itemize}
				\item position 
				\item velocity
			\end{itemize}
		\item update model
		\item R package \texttt{emma} 
	\end{itemize}
\end{graphicsFrame}

\begin{frame}{PSO variables}
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
		$c_{zr}$ [\SI{22}{\milli\mol/\liter}]	&$n_L$	&$T_{C}$[\SI{}{\degreeCelsius}]	&$v_{C}$[\SI{}{\milli\meter/\second}]	&$T_{cal}$[\SI{}{\degreeCelsius}]	&$v_{cal}$[\SI{}{\degreeCelsius/\hour}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}
\end{frame}

%	\begin{itemize}
%		\item Aluminium Contact through mask
%		\item Silver paste
%	\end{itemize}
%\end{frame}
%07. results measuring 
	% - SEM % check which sample 
\begin{graphicsFrame}{SEM micrographs}{}{0.37}{right}{sem}{}
		\begin{itemize}
			\item (a) first recipe on FTO
			\item (b) 10 layers on steel
			\item (c) cross section of 5 layers on FTO
			\item (d) side view of scratched layer on steel
		\end{itemize}
\end{graphicsFrame}

	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv1}{}\end{graphicsFrame}
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
	% - EMMA 
%08. results EMMA 
\begin{frame}{Pin Hole Density}\begin{figure}\includegraphics[width=.66\textwidth]{figures/phd.png}\end{figure}\end{frame}
\begin{frame}{Leakage Current}\begin{figure}\includegraphics[width=.66\textwidth]{figures/leakage.png}\end{figure}\end{frame}
\begin{frame}{PSO generations}\begin{figure}\includegraphics[width=.96\textwidth]{figures/emma-gen.png}\end{figure}\end{frame}
%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
	% - gen 
%09. comparison with other statistics 
	% - comparing with other stats

\begin{frame}{Comparison with Statistics}
\begin{table}[htb]
	\centering
%	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc }
    \hline\hline
        $\gamma$&  MAE(e)&   MSE(e)\\
    \hline
		PSO&   \textbf{10}& 171\\
        LR&    13& 250\\
        KRR &17 &548 \\
        SVM& 15&  415\\
    \hline\hline
	\end{tabular}
%}
	\pause
%	\vspace{1em}
%	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\rho$&  MAE(e)&   MSE(e)\\
    \hline
		PSO&   \textbf{0.14}&   0.03\\
        LR&    0.19&   0.06\\
        KRR &0.25 &0.12 \\
        SVM &0.23 &0.13 \\
    \hline\hline
	\end{tabular}
%}
%    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
	\label{tab:post-emma}
\end{table}
\end{frame}

>>>>

	%% ====== title page ======
	\title{Particle Swarm Optimization for Passivation of Steel Substrate with Zirconium Oxide} %% Presentation Title
	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
	\newcommand{\gPath}{figures/}									%% set graphics path
	\newcommand{\graphicsTitleBackground}{title}    %% Filename of background graphic

@@

\usepackage{siunitx}
\usepackage{chemformula}
\usepackage{upgreek}
\usepackage{physics}
\usepackage{xcolor}
\newcommand{\red}[1]{\textcolor{red}{#1}}

@@

%% ====== Slides ======
%TODO: - read aqua/good recipe/mars paper
%01. title slide 
	% - aufhänger
	% - AI and PV
	% - Lab or Computer 
%02. agenda
%\begin{frame}{The Iterative Process}
%	\begin{figure}
%		\center
%		\includegraphics[width=.8\textwidth]{figures/iteration.png}
%	\end{figure}
%\end{frame}
\begin{graphicsFrame}{}{}{0.1}{}{iteration}{}\end{graphicsFrame}
	\iffalse
\begin{frame}{Agenda}
	\vspace{2em}
	\begin{itemize}
		\item Motivation: CIGS substrate
		\item Methods: recipe and sample preparation
		\item Calculation: PSO and data pipeline
		\item Results: materials and optimisation
	\end{itemize}
\end{frame}
\fi
	% - more like process  from beginning to finish
%03. background info
	% - PV CIGS substrate % https://de.wikipedia.org/wiki/Chalkopyrit
	% https://en.wikipedia.org/wiki/Copper_indium_gallium_selenide_solar_cell
\iffalse
\begin{graphicsFrame}{Copper Indium Gallium Selenide (CIGS)}{}{0.37}{left}{cigs}{U. Rau, H.W. Schock (2013) "Solar Cells"}
\begin{table}
	\resizebox{.95\textwidth}{!}{
    \begin{tabular}{cccc}
        \hline\hline
		Empirical Formula&   Band Gap [\SI{}{\electronvolt}]\\
        \hline
		\ch{CuInSe2}&  1.04\\
		\ch{CuGaSe2}&  1.7\\
		\ch{CuInS2}&  1.5\\
		\ch{CuGaS2}&  1.55\\
        \hline\hline
    \end{tabular}
}
    \caption{Band gaps of different chalcopyrites (K. Mertens 2015 "Photovoltaik")}
\end{table}
\end{graphicsFrame}
\fi

@@

\begin{graphicsFrame}{Thin-Film Photovoltaics: CIGS modules}{}{0.1}{}{cigs_mod}{}
\end{graphicsFrame}

%04. hypothesis 
%05. manual methods
	% - precursor solution preparation 
		% Anwar 2017 https://iopscience.iop.org/article/10.1088/1757-899X/257/1/012087
		% Hu 2016 https://www.sciencedirect.com/science/article/abs/pii/S0272884216312548
\begin{frame}{Adaption of Precursor Solutions Recipe}
	\begin{figure}
		\includegraphics[width=.79\textwidth]{figures/huetal.png}
	\end{figure}
%	\pause
\begin{table}[h]
	\center
	\begin{tabular}{lll}
		\hline\hline
		recipe	&original	&adapted \\
		\hline
		solvent & \ch{EtOEt} & \ch{BuOH} \\
		precusor & \ch{Al(OPr^i)3} & \ch{Zr(OPr)4} \\
		chelating agent & \ch{AcAc} & \ch{AcAc} \\
		stabilzing agent & \ch{AcOH} & \ch{iPrOH}/\ch{AcOH}	\\
		\hline\hline
	\end{tabular}
	%\caption{Composition of different buthanolic solutions}
\end{table}
\end{frame}
%\iffalse
\begin{frame}{Different Precusor Concentrations}
	\begin{figure}
		\includegraphics[width=.79\textwidth]{figures/huetal.png}
	\end{figure}
\begin{table}[h]
	\center
	\label{tab:rec2}
	\begin{tabular}{rlllll}
		\hline\hline
		&\red{1x}		&2x		&3x		&4x		&5x		\\
		\hline
		\ch{BuOH} [ml]	&\red{4.95}	&4.9	&4.85	&4.8	&4.75	\\
		\ch{ZrPro} [ml]	&\red{0.05}	&0.1	&0.15	&0.2	&0.25	\\
		\ch{AcAc} [ml]	&\red{0.0125}	&0.025	&0.0375	&0.05	&0.0625	\\
		\ch{IPO}/\ch{AcOH} [ml]	&\red{2}		&2		&2		&2		&2		\\
		\hline\hline
	\end{tabular}
	%\caption{Composition of different buthanolic solutions}
\end{table}
%\fi
\end{frame}

	% - doctor blading = tape castig 
	% - calcination 
\begin{graphicsFrame}{Tape Casting and Calcination}{}{0.37}{left}{tc}{}

		\vspace{1em}
		\begin{itemize}
			\item Tape Casting
				\begin{itemize}
					\item temperature: 40-\SI{80}{\degreeCelsius}
					\item blade speed: 10-\SI{20}{\milli\meter/\second}
				\end{itemize}
				\vspace{1em}
			\item Calcination
				\begin{itemize}
					\item temperature: 300-\SI{500}{\degreeCelsius}
					\item heating rate: 2-\SI{12}{\degreeCelsius/\hour}
				\end{itemize}
		\end{itemize}
\end{graphicsFrame}

	% - SEM % check which sample 
\begin{graphicsFrame}{Cross Section of \ch{ZrO2}}{}{0.37}{right}{sem_cs}{}
	\vspace{3em}
		\begin{itemize}
			\item Scanning Electron Microscope 
			\item substrate: FTO (Fluorine Doped Tin Oxide)
			\item single layer of \ch{ZrO2}
		\end{itemize}
\end{graphicsFrame}

%\begin{frame}{Tape casting and Calcination}
%	\begin{figure}
%		\center
%		\includegraphics[width=.65\textwidth]{figures/tc.jpg}
%	\end{figure}
%\end{frame}
%	\begin{itemize}
%		\item doctor blading construction 
%		\item calcination infos (max temperatur, heating rate)
%	\end{itemize}
%\end{frame}
	% - sputtering contacts
	% - measuring current-voltage characteristics
\iffalse
\begin{frame}{Application of Contacts}
	\begin{figure}
		\includegraphics<1>[width=.63\textwidth]{figures/sample1.jpg}
		\includegraphics<2>[width=.63\textwidth]{figures/sample2.jpg}
		\includegraphics<3>[width=.63\textwidth]{figures/sample3.jpg}
	\end{figure}
\end{frame}
\fi
%\begin{graphicsFrame}{Application of Contacts}{}{0.37}{right}{sample1}{}
%		\begin{itemize}
%			\item Left: Shadow mask
%			\item Right: Steel substrate \ch{ZrO2} layer
%		\end{itemize}
%\end{graphicsFrame}
%
\begin{graphicsFrame}{Application of Contacts}{}{0.37}{left}{sput1}{}
		\begin{itemize}
			\item Bottom left: Shadow mask
			\item Bottom right: Steel substrate \ch{ZrO2} layer
			\item Top: samples with mask attached
		\end{itemize}
\end{graphicsFrame}
%
\begin{graphicsFrame}{Applied Contacts}{}{0.37}{right}{sample2}{}
	\vspace{1em}
		\begin{itemize}
			\item passivated sample with array of contacts
				\vspace{.5em}
			\item contacts to steel on edges
		\end{itemize}
\end{graphicsFrame}
%
\begin{graphicsFrame}{Measuring Current Voltage Characteristics}{}{0.37}{left}{sample3}{}
	\vspace{3em}
		\begin{itemize}
			\item left needle touches top contact (\ch{ZrO2})
				\vspace{1.5em}
			\item right needle touches bottom contact (steel)
		\end{itemize}
\end{graphicsFrame}

	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
\begin{graphicsFrame}{Current-Voltage characteristics}{}{0.37}{left}{iv-noi}{}
	\vspace{2em}
	\begin{itemize}
		\item voltage sweep
		\vspace{.5em}
		\item \SI{10}{\milli\volt} steps
		\vspace{.5em}
		\item very low current 
		\vspace{.5em}
		\item low conductivity 
		\vspace{.5em}
		\item high resistance 
	\end{itemize}
\end{graphicsFrame}
\begin{graphicsFrame}{Current-Voltage characteristics II}{}{0.37}{left}{iv-log}{}
	\vspace{2em}
	\begin{itemize}
		\item all measurements of single sample
		\vspace{.5em}
		\item huge range 
		\vspace{.5em}
		\item low current
		\vspace{.5em}
		\item high current
	\end{itemize}
\end{graphicsFrame}

%06. computational pipeline 
\begin{graphicsFrame}
	{Pin Hole Density and Leakage Current}
	{}{0.37}
	{left}{calc}{}
	\vspace{2em}
	\begin{itemize}
		\item Conductivity
			\begin{itemize}
				\item $
					g = \eval{\dv{I}{V}}_{V =0}
					$
			\end{itemize}
	\vspace{0.5em}
%	\pause
		\item Pin Hole Density 
			\begin{itemize}
				\item $
	s_i = \begin{cases}
		1 &\text{if} \quad g_i < 10^{-5} \\
		0 &\text{if} \quad g_i \geq 10^{-5} \\
%        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
%        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
	\end{cases}
					$
				\item $
	\rho = \sum_i^N \frac{s_i}{N}
					$
			\end{itemize}
	\vspace{0.5em}
%	\pause
		\item Leakage Current 
			\begin{itemize}
				\item $
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	$
			\end{itemize}
	\end{itemize}
\end{graphicsFrame}
	% - PSO + MARS = EMMA
	% PSO https://doi.org/10.1109/CEC.2010.5586165
\begin{graphicsFrame}{Particle Swarm Optimisation}{}{0.37}{right}{swarm}{}
	\vspace{3em}
	\begin{itemize}
		\item inspired by fish schools %# swarm intelligence
		\item iterative process % nice bcs sample prep takes long time 
		\item particles: 
			\begin{itemize}
				\item input vars: position 
				\item velocity
			\end{itemize}
%		\item update model
		\item R package \texttt{emma} 
	\end{itemize}
\end{graphicsFrame}

\begin{frame}{Input Variables for Optimisation}
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
		$c_{zr}$ [\SI{22}{\milli\mol/\liter}]	&$n_L$	&$T_{C}$[\SI{}{\degreeCelsius}]	&$v_{C}$[\SI{}{\milli\meter/\second}]	&$T_{cal}$[\SI{}{\degreeCelsius}]	&$v_{cal}$[\SI{}{\degreeCelsius/\hour}]	\\
		\hline
		\pause
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}
\end{frame}

%	\begin{itemize}
%		\item Aluminium Contact through mask
%		\item Silver paste
%	\end{itemize}
%\end{frame}
%07. results measuring 
%\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
%\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
	% - EMMA 
%08. results EMMA 
%\begin{frame}{Pin Hole Density}\begin{figure}\includegraphics[width=.66\textwidth]{figures/phd.png}\end{figure}\end{frame}
%\begin{frame}{Leakage Current}\begin{figure}\includegraphics[width=.66\textwidth]{figures/leakage.png}\end{figure}\end{frame}
\begin{frame}{PSO generations}\begin{figure}\includegraphics[width=.96\textwidth]{figures/emma-gen.png}\end{figure}\end{frame}
%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
	% - gen 
%09. comparison with other statistics 
	% - comparing with other stats

	\iffalse
\begin{frame}{Comparison with Statistics}
\begin{table}[htb]
	\centering
%	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc }
    \hline\hline
        $\gamma$&  MAE&   MSE\\
    \hline
		PSO&   \textbf{10}& 171\\
        LR&    13& 250\\
        KRR &17 &548 \\
        SVM& 15&  415\\
    \hline\hline
	\end{tabular}
%}
	\pause
%	\vspace{1em}
%	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\rho$&  MAE&   MSE\\
    \hline
		PSO&   \textbf{0.14}&   0.03\\
        LR&    0.19&   0.06\\
        KRR &0.25 &0.12 \\
        SVM &0.23 &0.13 \\
    \hline\hline
	\end{tabular}
%}
%    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
	\label{tab:post-emma}
\end{table}
\end{frame}
\fi
